Coalition Formation Algorithm of Prosumers in a Smart Grid Environment

### 2014-09-23 Article.tex
update table 1
update

Due to the volatile nature of DER productions or user consumptions, the available power of a coalition will oscillates around $ P_{S}^{CRCT} $. It will be the responsability of the coalition, that is the information system maintaining the coalition, to compensate for deviations. In this paper, we consider then that the smaller these deviations, the better. Based on the $ \mathcal{T}_{S} $ distribution, the probability of S value (at any instant t) being below its contract value $ Pr[P_{S}(t) \leq P_{S}^{CRCT} ] $ appears therefore as a quantity of interest that we would want to keep as low as possible.

@@

We then consider another constraint denoted by $ P^{MIN} $, as the \textbf{minimum contract value}, which states that only coalitions with higher contract values ($ P_{S}^{CRCT} \geq P^{MIN} $) will be accepted. Figure \ref{Fig89} summurizes the main notations of this paper.

@@

\begin{table}[!t]
\label{Fig89}
\centering
\scriptsize
\begin{tabular}{l|p{4.5cm}}
  \hline
  \textbf{Symbols} &  \\
  \hline 
  $ \mathcal{A}=\{a_{1},...,a_{N}\} $ & Set of agents \\
  $ P_{i}(t) \in \mathbb{R}\ \ (P_{S}(t)) $ & Instantaneous production of agent $i$ in coalition $S$ at time $t$ \\
  $ \mathcal{T}_{i} = \{P_{i}(t_{0}),...,P_{i}(t_{K})\} $ & Time series of agent i available production values \\
  $ \mathcal{P}_{i}\ \ (\mathcal{P}_{S}) $ & Probability distribution of the production of the agent i in coalition S\\
  $ \phi \in [0,1] $ & Reliability threshold \\
  $ P^{MIN} \in \mathbb{R}^+ $ & Min value threshold \\
  $ P_{S}^{CRCT} \in \mathbb{R}^+ $ & Contract value of coalition S \\
  $ P_{\phi}(S) \in \mathbb{R}^+ $ & Max contract value under $ \phi $ constraint \\
  $ \mathcal{U}_{\phi,\ P^{MIN}}(S) $ & Utility function \\
  $ \tau_{i}(S) \in \mathbb{R}$ & Decision rule for mapping overlapping into disjoint coalitions \\
  $ \epsilon \in [0,1] $ & Pruning threshold for the correlation graph \\
  $ N_{COAL} \in \mathbb{Z}^+ $ & Number of desired coalition \\
  $ CS = \{S_{1},...,S_{N_{COAL}}\} $ & Coalition structure \\
  \hline
\end{tabular}
\caption{Notations}
\end{table}

>>>>

Due to the volatile nature of DER productions or user consumptions, the available power of a coalition will oscillates around $ P_{S}^{CRCT} $. It will be the responsibility of the coalition, that is the information system maintaining the coalition, to compensate for deviations. In this paper, we consider then that the smaller these deviations, the better. Based on the $ \mathcal{T}_{S} $ distribution, the probability of S value (at any instant t) being below its contract value $ Pr[P_{S}(t) \leq P_{S}^{CRCT} ] $ appears therefore as a quantity of interest that we would want to keep as low as possible.

@@

We then consider another constraint denoted by $ P^{MIN} $, as the \textbf{minimum contract value}, which states that only coalitions with higher contract values ($ P_{S}^{CRCT} \geq P^{MIN} $) will be accepted. In table \ref{table1} summarizes the main notations of this paper.

@@

\begin{table}[!t]
\centering
\scriptsize
\begin{tabular}{l|p{4.5cm}}
  \hline 
  $ \mathcal{A}=\{a_{1},...,a_{N}\} $ & Set of agents \\
  $ P_{i}(t) \in \mathbb{R}\ \ (P_{S}(t)) $ & Instantaneous production of agent $i$ in coalition $S$ at time $t$ \\
  $ \mathcal{T}_{i} = \{P_{i}(t_{0}),...,P_{i}(t_{K})\} $ & Time series of agent i available production values \\
  $ \mathcal{P}_{i}\ \ (\mathcal{P}_{S}) $ & Probability distribution of the production of the agent i in coalition S\\
  $ \phi \in [0,1] $ & Reliability threshold \\
  $ P^{MIN} \in \mathbb{R}^+ $ & Min value threshold \\
  $ P_{S}^{CRCT} \in \mathbb{R}^+ $ & Contract value of coalition S \\
  $ P_{\phi}(S) \in \mathbb{R}^+ $ & Max contract value under $ \phi $ constraint \\
  $ \mathcal{U}_{\phi,\ P^{MIN}}(S) $ & Utility function \\
  $ \tau_{i}(S) \in \mathbb{R}$ & Decision rule for mapping overlapping into disjoint coalitions \\
  $ \epsilon \in [0,1] $ & Pruning threshold for the correlation graph \\
  $ N_{COAL} \in \mathbb{Z}^+ $ & Number of desired coalition \\
  $ CS = \{S_{1},...,S_{N_{COAL}}\} $ & Coalition structure \\
  \hline
\end{tabular}
\caption{Notations\label{table1}}
\end{table}
